Active Learning for SAT-Solver Benchmarking

### 2022-09-26 paper/paper.tex
Sort LaTeX imports and remove unused ones
Just for fun.
Fix overfull boxes in plots/tables
... but not the overfull boxes in main text, as the latter is very likely
to change.

\usepackage[T1]{fontenc} % recommended by LNCS template
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage{tablefootnote}
\usepackage{array}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\DontPrintSemicolon
\def\NlSty#1{\textnormal{\fontsize{8}{10}\selectfont{}#1}}
\SetKwSty{texttt}
\SetCommentSty{emph}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.26\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.1,2.4) {GAN};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

@@

\begin{table}[tbp]
  \centering
  \caption{PAR-2 ranking vs. ranking based on discretized runtimes for the SAT Competition~2022 Anniversary Track instances~\cite{sat2022} ($k = 3$; hierarchical clustering)}
  \label{tab:discreteranking}
  \vspace{0.2cm}
  \begin{tabular}{
    c
    >{\centering\arraybackslash}p{2.2cm}p{3.6cm}
    >{\centering\arraybackslash}p{1.8cm}p{3.3cm}
  }
    \hline
    Rank & \multicolumn{2}{c}{PAR-2 Ranking} & \multicolumn{2}{c}{Cluster-Label Ranking} \\
    \hline
1   & 2806.400 & Kissat\_MAB\_ESA           & 1.172 & Kissat\_MAB\_ESA \\
2   & 2810.959 & kissat-sc2022-bulky        & 1.183 & kissat-sc2022-bulky \\
3   & 2830.143 & ekissat-mab-gb-db          & 1.185 & ekissat-mab-gb-db \\
\cellcolor{gray!15} 4   & \cellcolor{gray!15} 2833.081 & \cellcolor{gray!15} Kissat\_MAB\_UCB           & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} kissat\_inc \\
\cellcolor{gray!15} 5   & \cellcolor{gray!15} 2833.397 & \cellcolor{gray!15} kissat\_inc                & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} Kissat\_MAB\_UCB \\
6   & 2841.734 & ekissat-mab-db-v1          & 1.192 & ekissat-mab-db-v1 \\
7   & 2842.666 & Kissat\_MAB\_MOSS          & 1.192 & Kissat\_MAB\_MOSS \\
8   & 2857.219 & Kissat\_MAB-HyWalk         & 1.195 & Kissat\_MAB-HyWalk \\
9   & 2866.960 & kissat-sc2022-light        & 1.120 & kissat-sc2022-light \\
10  & 2896.371 & kissat-els-v2              & 1.216 & kissat-els-v2 \\
11  & 2950.179 & hKis-unsat                 & 1.229 & hKis-unsat \\
12  & 2964.729 & Kissat\_adaptive\_restart  & 1.234 & Kissat\_adaptive\_restart \\
13  & 2974.990 & SeqFROST-NoExtend          & 1.247 & SeqFROST-NoExtend \\
14  & 3010.642 & Cadical\_ESA               & 1.248 & Cadical\_ESA \\
\cellcolor{gray!15} 15  & \cellcolor{gray!15} 3012.152 & \cellcolor{gray!15} kissat-els-v1              & \cellcolor{gray!15} 1.258 & \cellcolor{gray!15} CadicalReorder \\
\cellcolor{gray!15} 16  & \cellcolor{gray!15} 3028.922 & \cellcolor{gray!15} CadicalReorder             & \cellcolor{gray!15} 1.264 & \cellcolor{gray!15} kissat-els-v1 \\
\cellcolor{gray!15} 17  & \cellcolor{gray!15} 3042.540 & \cellcolor{gray!15} cadical\_rel\_Scavel       & \cellcolor{gray!15} 1.278 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1 \\
\cellcolor{gray!15} 18  & \cellcolor{gray!15} 3082.293 & \cellcolor{gray!15} kissat\_relaxed            & \cellcolor{gray!15} 1.283 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2 \\
\cellcolor{gray!15} 19  & \cellcolor{gray!15} 3089.304 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1          & \cellcolor{gray!15} 1.298 & \cellcolor{gray!15} kissat\_relaxed \\
\cellcolor{gray!15} 20  & \cellcolor{gray!15} 3095.118 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2          & \cellcolor{gray!15} 1.361 & \cellcolor{gray!15} cadical\_rel\_Scavel \\
21  & 3272.674 & glucose-reboot             & 1.379 & glucose-reboot \\
\cellcolor{gray!15} 22  & \cellcolor{gray!15} 3287.322 & \cellcolor{gray!15} LStech-Maple-HyWalk        & \cellcolor{gray!15} 1.414 & \cellcolor{gray!15} hCaD\_V1-psids \\
23  & 3288.798 & LSTech\_Maple              & 1.446 & LSTech\_Maple \\
\cellcolor{gray!15} 24  & \cellcolor{gray!15} 3399.281 & \cellcolor{gray!15} SLIME-SC-2022-beta         & \cellcolor{gray!15} 1.469 & \cellcolor{gray!15} LStech-Maple-HyWalk \\
\cellcolor{gray!15} 25  & \cellcolor{gray!15} 3410.345 & \cellcolor{gray!15} SLIME-SC-2022              & \cellcolor{gray!15} 1.470 & \cellcolor{gray!15} SLIME-SC-2022-beta \\
\cellcolor{gray!15} 26  & \cellcolor{gray!15} 3430.403 & \cellcolor{gray!15} hCaD\_V1-psids             & \cellcolor{gray!15} 1.523 & \cellcolor{gray!15} SLIME-SC-2022 \\
27  & 3504.244 & MapleLCMDistChrBt-DL-v3    & 1.542 & MapleLCMDistChrBt-DL-v3 \\
28  & 4750.808 & IsaSAT                     & 2.062 & IsaSAT \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[tb!]
  \centering
  \caption{Pareto-optimal approaches for different choices of $\delta$ regarding our smaller hyper-parameter tuning dataset. Rows with no changes in comparison to their predecessor are hidden. Ranking approaches are either predicted cluster-label ranking (Pred.) or partially observed PAR-2 ranking (PAR-2). Selection approaches are either uncertainty-based selection (Uncert.) or information-gain-based selection (IG). Stopping criteria are either ranking convergence (Conv.) or Wilcoxon-based (Wilcoxon).}
  \label{tab:paretotable}
  \vspace{0.2cm}
  \begin{tabular}{
    >{\centering\arraybackslash}m{0.4cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
  }
    \hline
    $\delta$ & Ranking & Selection & Stopping & Fraction Runtime ($O_{\operatorname{rt}}$) & Fraction Instances & $O_{\operatorname{acc}}$ & $O_{\delta}$ \\
    \hline
    0.00 & PAR-2 & Uncert. & Conv. & 0.021 & 0.025 & 0.593 & 0.979 \\
    0.05 & Pred. & Uncert. & Conv. & 0.024 & 0.158 & 0.765 & 0.966 \\
    0.10 & Pred. & Uncert. & Conv. & 0.025 & 0.128 & 0.779 & 0.955 \\
    0.15 & Pred. & IG & Conv. & 0.028 & 0.112 & 0.802 & 0.946 \\
    $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ \\
    0.50 & Pred. & IG & Conv. & 0.028 & 0.112 & 0.802 & 0.887 \\
    0.55 & Pred. & Uncert. & Conv. & 0.053 & 0.142 & 0.824 & 0.880 \\
    0.60 & Pred. & Uncert. & Conv. & 0.146 & 0.082 & 0.897 & 0.880 \\
    $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ \\
    0.75 & Pred. & Uncert. & Conv. & 0.146 & 0.082 & 0.897 & 0.886 \\
    0.80 & Pred. & Uncert. & Conv. & 0.219 & 0.128 & 0.917 & 0.890 \\
    \hline
    0.85 & Pred. & Uncert. & Conv. & 0.272 & 0.171 & 0.927 & 0.897 \\
    \hline
    0.90 & Pred. & Uncert. & Wilcoxon & 0.894 & 0.888 & 0.996 & 0.907 \\
    0.95 & Pred. & Uncert. & Wilcoxon & 0.931 & 0.924 & 1.000 & 0.953 \\
    1.00 & Pred. & Uncert. & Wilcoxon & 0.989 & 0.981 & 1.000 & 1.000 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[tb!]
  \centering
  \caption{Top-10 most \textit{important} families regarding the average occurrences and the fraction of selected occurrences regarding our AL approach}
  \label{tab:families}
  \hspace{-0.58cm}
  \begin{subtable}{0.45\textwidth}
    \centering
    \caption{Sorted by the average number of occurrences}
    \label{tab:familiesa}

    \begin{tabular}{
      >{\centering\arraybackslash}m{1.6cm}
      >{\centering\arraybackslash}m{1.3cm}
      >{\centering\arraybackslash}m{1.3cm}
      >{\centering\arraybackslash}m{1.3cm}
    }
      \hline
      Family & Avg. Occ. & In Dataset & Fraction (\%) \\
      \hline
      planning              & 19.14 &  333 &  5.7 \\
      subgraph-isomorphism  & 16.27 &  175 &  9.3 \\
      crypto-graphy         & 13.11 &  311 &  4.2 \\
      pigeon-hole           &  7.55 &  151 &  5.0 \\
      fpga-routing          &  6.16 &  73  &  8.4 \\
      rbsat                 &  5.93 &  113 &  5.2 \\
      quasigroup-completion &  5.23 &  210 &  2.5 \\
      unknown               &  4.93 &  169 &  2.9 \\
      miter                 &  4.84 &  199 &  2.4 \\
      bitvector             &  4.73 &  214 &  2.2 \\
      % clique-coloring       &  4.21 &  64  &  0.066 \\
      % mosoi-289             &  3.75 &  31  &  0.121 \\
      % hardware-verification &  3.70 &  344 &  0.011 \\
      % hardware-bmc          &  2.77 &  78  &  0.035 \\
      % graph-based           &  2.77 &  134 &  0.021 \\
      % coloring              &  2.66 &  41  &  0.065 \\
      % waerden               &  2.55 &  43  &  0.059 \\
      % graph-coloring        &  2.50 &  87  &  0.029 \\
      % auto-correlation      &  2.39 &  46  &  0.052 \\
      % knights-problem       &  2.25 &  17  &  0.132 \\
      %\hline
      Remaining families    & 104.45 & 3407 & 3.1 \\
      \hline
      Sum                   & 192.34 & 5355 & 3.6 \\
      \hline
    \end{tabular}
  \end{subtable}
  \hspace{0.55cm}
  \begin{subtable}{0.45\textwidth}
    \centering
    \caption{Sorted by the fraction of sampled occurrences}
    \label{tab:familiesb}

>>>>

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tablefootnote}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

\newcommand{\cmark}{\ding{51}} % symbols for table comparing benchmarking approaches
\newcommand{\xmark}{\ding{55}}

\DontPrintSemicolon % configuration for algorithm2e
\def\NlSty#1{\textnormal{\fontsize{8}{10}\selectfont{}#1}}
\SetKwSty{texttt}
\SetCommentSty{emph}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.25\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.35\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.35\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.1,2.4) {GAN};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

@@

\begin{table}[tbp]
  \centering
  \caption{PAR-2 ranking vs. ranking based on discretized runtimes for the SAT Competition~2022 Anniversary Track instances~\cite{sat2022} ($k = 3$; hierarchical clustering)}
  \label{tab:discreteranking}
  \begin{tabular}{
    c
    >{\centering\arraybackslash}p{1.8cm}p{3.6cm}
    >{\centering\arraybackslash}p{1.8cm}p{3.6cm}
  }
    \hline
    Rank & \multicolumn{2}{c}{PAR-2 Ranking} & \multicolumn{2}{c}{Cluster-Label Ranking} \\
    \hline
1   & 2806.400 & Kissat\_MAB\_ESA           & 1.172 & Kissat\_MAB\_ESA \\
2   & 2810.959 & kissat-sc2022-bulky        & 1.183 & kissat-sc2022-bulky \\
3   & 2830.143 & ekissat-mab-gb-db          & 1.185 & ekissat-mab-gb-db \\
\cellcolor{gray!15} 4   & \cellcolor{gray!15} 2833.081 & \cellcolor{gray!15} Kissat\_MAB\_UCB           & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} kissat\_inc \\
\cellcolor{gray!15} 5   & \cellcolor{gray!15} 2833.397 & \cellcolor{gray!15} kissat\_inc                & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} Kissat\_MAB\_UCB \\
6   & 2841.734 & ekissat-mab-db-v1          & 1.192 & ekissat-mab-db-v1 \\
7   & 2842.666 & Kissat\_MAB\_MOSS          & 1.192 & Kissat\_MAB\_MOSS \\
8   & 2857.219 & Kissat\_MAB-HyWalk         & 1.195 & Kissat\_MAB-HyWalk \\
9   & 2866.960 & kissat-sc2022-light        & 1.120 & kissat-sc2022-light \\
10  & 2896.371 & kissat-els-v2              & 1.216 & kissat-els-v2 \\
11  & 2950.179 & hKis-unsat                 & 1.229 & hKis-unsat \\
12  & 2964.729 & Kissat\_adaptive\_restart  & 1.234 & Kissat\_adaptive\_restart \\
13  & 2974.990 & SeqFROST-NoExtend          & 1.247 & SeqFROST-NoExtend \\
14  & 3010.642 & Cadical\_ESA               & 1.248 & Cadical\_ESA \\
\cellcolor{gray!15} 15  & \cellcolor{gray!15} 3012.152 & \cellcolor{gray!15} kissat-els-v1              & \cellcolor{gray!15} 1.258 & \cellcolor{gray!15} CadicalReorder \\
\cellcolor{gray!15} 16  & \cellcolor{gray!15} 3028.922 & \cellcolor{gray!15} CadicalReorder             & \cellcolor{gray!15} 1.264 & \cellcolor{gray!15} kissat-els-v1 \\
\cellcolor{gray!15} 17  & \cellcolor{gray!15} 3042.540 & \cellcolor{gray!15} cadical\_rel\_Scavel       & \cellcolor{gray!15} 1.278 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1 \\
\cellcolor{gray!15} 18  & \cellcolor{gray!15} 3082.293 & \cellcolor{gray!15} kissat\_relaxed            & \cellcolor{gray!15} 1.283 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2 \\
\cellcolor{gray!15} 19  & \cellcolor{gray!15} 3089.304 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1          & \cellcolor{gray!15} 1.298 & \cellcolor{gray!15} kissat\_relaxed \\
\cellcolor{gray!15} 20  & \cellcolor{gray!15} 3095.118 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2          & \cellcolor{gray!15} 1.361 & \cellcolor{gray!15} cadical\_rel\_Scavel \\
21  & 3272.674 & glucose-reboot             & 1.379 & glucose-reboot \\
\cellcolor{gray!15} 22  & \cellcolor{gray!15} 3287.322 & \cellcolor{gray!15} LStech-Maple-HyWalk        & \cellcolor{gray!15} 1.414 & \cellcolor{gray!15} hCaD\_V1-psids \\
23  & 3288.798 & LSTech\_Maple              & 1.446 & LSTech\_Maple \\
\cellcolor{gray!15} 24  & \cellcolor{gray!15} 3399.281 & \cellcolor{gray!15} SLIME-SC-2022-beta         & \cellcolor{gray!15} 1.469 & \cellcolor{gray!15} LStech-Maple-HyWalk \\
\cellcolor{gray!15} 25  & \cellcolor{gray!15} 3410.345 & \cellcolor{gray!15} SLIME-SC-2022              & \cellcolor{gray!15} 1.470 & \cellcolor{gray!15} SLIME-SC-2022-beta \\
\cellcolor{gray!15} 26  & \cellcolor{gray!15} 3430.403 & \cellcolor{gray!15} hCaD\_V1-psids             & \cellcolor{gray!15} 1.523 & \cellcolor{gray!15} SLIME-SC-2022 \\
27  & 3504.244 & MapleLCMDistChrBt-DL-v3    & 1.542 & MapleLCMDistChrBt-DL-v3 \\
28  & 4750.808 & IsaSAT                     & 2.062 & IsaSAT \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[tb!]
  \centering
  \caption{Pareto-optimal approaches for different choices of $\delta$ regarding our smaller hyper-parameter tuning dataset. Rows with no changes in comparison to their predecessor are hidden. Ranking approaches are either predicted cluster-label ranking (Pred.) or partially observed PAR-2 ranking (PAR-2). Selection approaches are either uncertainty-based selection (Uncert.) or information-gain-based selection (IG). Stopping criteria are either ranking convergence (Conv.) or Wilcoxon-based (Wilcoxon).}
  \label{tab:paretotable}
  \vspace{0.2cm}
  \begin{tabular}{
    >{\centering\arraybackslash}m{0.6cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.6cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
    >{\centering\arraybackslash}m{1.5cm}
  }
    \hline
    $\delta$ & Ranking & Selection & Stopping & Fraction Runtime ($O_{\operatorname{rt}}$) & Fraction Instances & $O_{\operatorname{acc}}$ & $O_{\delta}$ \\
    \hline
    0.00 & PAR-2 & Uncert. & Conv. & 0.021 & 0.025 & 0.593 & 0.979 \\
    0.05 & Pred. & Uncert. & Conv. & 0.024 & 0.158 & 0.765 & 0.966 \\
    0.10 & Pred. & Uncert. & Conv. & 0.025 & 0.128 & 0.779 & 0.955 \\
    0.15 & Pred. & IG & Conv. & 0.028 & 0.112 & 0.802 & 0.946 \\
    $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ \\
    0.50 & Pred. & IG & Conv. & 0.028 & 0.112 & 0.802 & 0.887 \\
    0.55 & Pred. & Uncert. & Conv. & 0.053 & 0.142 & 0.824 & 0.880 \\
    0.60 & Pred. & Uncert. & Conv. & 0.146 & 0.082 & 0.897 & 0.880 \\
    $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ \\
    0.75 & Pred. & Uncert. & Conv. & 0.146 & 0.082 & 0.897 & 0.886 \\
    0.80 & Pred. & Uncert. & Conv. & 0.219 & 0.128 & 0.917 & 0.890 \\
    \hline
    0.85 & Pred. & Uncert. & Conv. & 0.272 & 0.171 & 0.927 & 0.897 \\
    \hline
    0.90 & Pred. & Uncert. & Wilcoxon & 0.894 & 0.888 & 0.996 & 0.907 \\
    0.95 & Pred. & Uncert. & Wilcoxon & 0.931 & 0.924 & 1.000 & 0.953 \\
    1.00 & Pred. & Uncert. & Wilcoxon & 0.989 & 0.981 & 1.000 & 1.000 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[tb!]
  \centering
  \caption{Top-10 most \textit{important} families regarding the average occurrences and the fraction of selected occurrences regarding our AL approach}
  \label{tab:families}
  \begin{subtable}[t]{0.48\textwidth}
    \centering
    \caption{Sorted by the average number of occurrences}
    \label{tab:familiesa}

    \begin{tabular}{
      >{\centering\arraybackslash}m{1.8cm}
      >{\centering\arraybackslash}m{1.2cm}
      >{\centering\arraybackslash}m{1.2cm}
      >{\centering\arraybackslash}m{1.2cm}
    }
      \hline
      Family & Avg. Occ. & In Dataset & Fraction (\%) \\
      \hline
      planning              & 19.14 &  333 &  5.7 \\
      subgraph-isomorphism  & 16.27 &  175 &  9.3 \\
      crypto-graphy         & 13.11 &  311 &  4.2 \\
      pigeon-hole           &  7.55 &  151 &  5.0 \\
      fpga-routing          &  6.16 &  73  &  8.4 \\
      rbsat                 &  5.93 &  113 &  5.2 \\
      quasigroup-completion &  5.23 &  210 &  2.5 \\
      unknown               &  4.93 &  169 &  2.9 \\
      miter                 &  4.84 &  199 &  2.4 \\
      bitvector             &  4.73 &  214 &  2.2 \\
      % clique-coloring       &  4.21 &  64  &  0.066 \\
      % mosoi-289             &  3.75 &  31  &  0.121 \\
      % hardware-verification &  3.70 &  344 &  0.011 \\
      % hardware-bmc          &  2.77 &  78  &  0.035 \\
      % graph-based           &  2.77 &  134 &  0.021 \\
      % coloring              &  2.66 &  41  &  0.065 \\
      % waerden               &  2.55 &  43  &  0.059 \\
      % graph-coloring        &  2.50 &  87  &  0.029 \\
      % auto-correlation      &  2.39 &  46  &  0.052 \\
      % knights-problem       &  2.25 &  17  &  0.132 \\
      %\hline
      Remaining families    & 104.45 & 3407 & 3.1 \\
      \hline
      Sum                   & 192.34 & 5355 & 3.6 \\
      \hline
    \end{tabular}
  \end{subtable}
  \hfill
  \begin{subtable}[t]{0.48\textwidth}
    \centering
    \caption{Sorted by the fraction of sampled occurrences}
    \label{tab:familiesb}
